### 2015-07-06 narrative/data-description.tex
Polishing data description section

\subsection{Data Description}
In order for the middleware and storage layer to understand data, I/O
intentions, and act accordingly, data must be described in a way that can be
understood by the system. In this project, we use the label the smallest unit of data
saved in the storage system as a \textit{chunk}.  A chunk consists of raw
data and metadata.  A user space variable, such as \textit{temperature}, may
consist of a collection of chunks, possibly with different accuracy or
resolution, with each chunk representing a different portion of the variable.
A key advantage of having attributes at this lowest level is that data
semantics, user intentions, QoS requirements, and the relationship between user
data to be readily captured and embedded with the raw data so that these
smallest pieces can each be managed independently or collectively, depending on
the need. As an example, retrieving 3D field data generated from a simulation
and then visualizing it requires the coordinates and connectivity variable be
accessed both together and with low latency to achieve a good user experience.
The data description, as enabled by managing data at this smallest level,
bridges the semantics gap between applications, middleware, and storage
systems and allows the system to understand user-level data, execute QoS
requirements and policies, and optimize application and system performance.

>>>>

\subsection{Data Description}
In order for the middleware and storage layer to make decisions
that are appropriate given the user's intentions, data must be
described in a way that communicates these intentions to
the system. In this project, we label the smallest unit of data
saved in the storage system as a \textit{chunk}.  A chunk consists of not only
raw data, but also metadata that expresses additional
knowledge about that data.
A user space variable, such as \textit{temperature}, may
consist of a collection of chunks, possibly with different accuracy or
resolution, and with each chunk representing
a different portion of the variable.
A key advantage of having attributes at this lowest level is that it allows data
semantics, user intentions, QoS requirements, and the relationship between user
data to be readily captured and embedded with the raw data so that these
smallest pieces can each be managed independently or collectively, depending on
the need. As an example, retrieving 3D field data generated from a simulation
and then visualizing it requires the coordinates and connectivity variables be
accessed simultaneously and with low latency to achieve a good user experience.
Managing data at this low level
bridges the semantics gap between applications, middleware, and storage
systems and allows the system to understand user-level data, execute QoS
requirements and policies, and optimize application and system performance.
